Higher order unification for free!

### 2024-04-09 paper/main.tex
rephrase of a sentence

\newcommand{\occursrigid}{\emph{occurs-rigidly}}
\newcommand{\occurrigid}{\emph{occur-rigidly}}
\begin{definition}[\occursrigid]\label{def:occrigid}
  A name $x$ \occursrigid{} in a $\beta$-normal term $t$, if $\forall \rho, x \in
  \subterm{\rho t}$
\end{definition}

\noteD{Not too clear?}
In other words $x$ \emph{\occursrigid} in $t$ if it occurs in $t$
outside of the scope of unification variables since an instantiation
is allowed to discard $x$ from the scope of the unification variable.
Note that $\eta$-contraction cannot make $x$ disappear, since the
variables being erased by $\eta$-contraction are locally bound inside $t$.

>>>>

\newcommand{\occursrigid}{\emph{occurs-rigidly}\xspace}
\newcommand{\occurrigid}{\emph{occur-rigidly}\xspace}
\begin{definition}[\occursrigid]\label{def:occrigid}
  A name $x$ \occursrigid{} in a $\beta$-normal term $t$, if $\forall \rho, x \in
  \subterm{\rho t}$
\end{definition}

In other words $x$ \occursrigid in $t$ if it occurs in $t$
outside of the scope of a unification variable $X$, otherwise an instantiation
of $X$ can make $x$ disappears from $t$.
Moreover, note that $\eta$-contracting $t$ cannot make $x$ disappear, since
$x$ is not a locally bound variable inside $t$.
